Reliable analytic approximation of pseudo-$\cl$ covariances

### 2019-05-18 draft/paper.tex
added paragraph about chi2 dists for TTTT and EEEE

% The simulations were generated as follow. First, we starts from some realistic
% large scale structure power spectra ($\clth$) and mask, which determines the
% number of modes. To this theoretical power spectra, in some cases, we
% added some foregrounds to study their impact on the approximated covariances.
% The mock power spectra was computed as follows:
% \begin{eqnarray}
%   \clf = A (l + 1)^\beta\,,
% \end{eqnarray}
% where $A$ was fixed so that $\clf/\clth = 0.1$ at $l=400$ and $\beta$ was
% randomly chosen from $U[-3, -1)$ for large scale effects and fixed to $\beta =
% 0$ for small scale ones.

>>>>

Apart from checking that we recover the same cosmological predictions from the
covariance matrices from both the analytical approximation and the
simulations, we studied the differences between them.

In this sense, one can see in Fig.~\ref{fig:TTTT_EEEE_chi2} that, we fully
recover the $\chi^2$ distribution (defining $\chi^2 = \cl - \langle \cl
\rangle C^{-1} \cl - \langle \cl \rangle$) for the TTTT case; whereas for the
worst case (i.e. EEEE) we are able to recover its shape, although sifted
toward lower values. This might be consequence of the fact that the inverse of
the covariance matrix is biased. It is interesting to note that even
the approximation of the mixing matrix as that of the case with spin 0, gives
good results.

\begin{figure*} %[htb]
  \centering
  \includegraphics[width=\columnwidth]{./figures/run_sph_ALL_TTTT_chi2.png}~
  \includegraphics[width=\columnwidth]{./figures/run_sph_ALL_EEEE_chi2.png}
  \caption{Comparison of the distributions found using different
    covariances for the TTTT (left) and EEEE (right) cases.}
  \label{fig:TTTT_EEEE_chi2}
\end{figure*}
